---
title: 'Supplementary Material for "A multivariate framework for analyzing spatial ordinal survey-based data / A multivariate spatial model for ordinal survey-based data" - Model assessment'
author: |
 | \Large Beltrán-Sánchez, MA$^1$; Martínez-Beneito, MA$^2$; Corberán-Vallet, A$^3$
 | $^1$angel.beltran@uv.es; $^2$miguel.a.martinez@uv.es; $^3$ana.corberan@uv.es
 | Department of Statistics and Operations Research, University of Valencia, Spain
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Multivariate modeling with independent responses

```{r}
indep <- readRDS(file = file.path("..", "results", "multi", "multi-2022-nimble-MH-indep-assessment.rds"))
```

### Multivariate modeling with correlated responses

```{r}
corr <- readRDS(file = file.path("..", "results", "multi", "multi-2022-nimble-MH-corr-assessment.rds"))
```

### Multivariate modeling with correlated responses and individual random effects

```{r}
corrire <- readRDS(file = file.path("..", "results", "multi", "multi-2022-nimble-MH-corr-ire-assessment.rds"))
```

### Variable P8_1: Have you been able to concentrate on what you were doing?

```{r}
Var <- 1
```


| Municipality          | More than usual                | Same as usual                     | Less than usual                  | Much less than usual                      |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_2: Have you lost a lot of sleep because of worries?

```{r}
Var <- 2
```


| Municipality          | Not at all                 | No more than usual                    | Rather more than usual                  | Much more than usual                |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_3: Have you felt that you have been playing a useful role in life?

```{r}
Var <- 3
```

| Municipality          | More than usual                | Same as usual                     | Less than usual                  | Much less than usual                      |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_4: Have you felt capable of making decisions?

```{r}
Var <- 4
```

| Municipality          | More than usual                | Same as usual                     | Less than usual                  | Much less than usual                      |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_5: Have you constantly felt overwhelmed and under stress?

```{r}
Var <- 5
```

| Municipality          | Not at all                 | No more than usual                    | Rather more than usual                  | Much more than usual                |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_6: Have you felt unable to overcome your difficulties?

```{r}
Var <- 6
```

| Municipality          | Not at all                 | No more than usual                    | Rather more than usual                  | Much more than usual                |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_7: Have you been able to enjoy your daily activities?

```{r}
Var <- 7
```

| Municipality          | More than usual                | Same as usual                     | Less than usual                  | Much less than usual                      |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_8: Have you been able to face up to your problems?

```{r}
Var <- 8
```

| Municipality          | More than usual                | Same as usual                     | Less than usual                  | Much less than usual                      |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_9: Have you felt unhappy or depressed?

```{r}
Var <- 9
```

| Municipality          | Not at all                 | No more than usual                    | Rather more than usual                  | Much more than usual                |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_10: Have you lost confidence in yourself?

```{r}
Var <- 10
```

| Municipality          | Not at all                 | No more than usual                    | Rather more than usual                  | Much more than usual                |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_11: Have you felt that you are a worthless person?

```{r}
Var <- 11
```

| Municipality          | Not at all                 | No more than usual                    | Rather more than usual                  | Much more than usual                |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

### Variable P8_12: Have you felt reasonably happy, considering all the circumstances?

```{r}
Var <- 12
```

| Municipality          | More than usual                | Same as usual                     | Less than usual                  | Much less than usual                      |
|----------------------|--------------------------|--------------------------|--------------------------|--------------------------|
| **Valencia**        | `r indep[[1]]$mean[Var, 1]` (`r indep[[1]]$PI$lower[Var, 1]`-`r indep[[1]]$PI$upper[Var, 1]`) <br> `r corr[[1]]$mean[Var, 1]` (`r corr[[1]]$PI$lower[Var, 1]`-`r corr[[1]]$PI$upper[Var, 1]`) <br> `r corrire[[1]]$mean[Var, 1]` (`r corrire[[1]]$PI$lower[Var, 1]`-`r corrire[[1]]$PI$upper[Var, 1]`) <br> **`r corrire[[1]]$real[Var, 1]`** | `r indep[[1]]$mean[Var, 2]` (`r indep[[1]]$PI$lower[Var, 2]`-`r indep[[1]]$PI$upper[Var, 2]`) <br> `r corr[[1]]$mean[Var, 2]` (`r corr[[1]]$PI$lower[Var, 2]`-`r corr[[1]]$PI$upper[Var, 2]`) <br> `r corrire[[1]]$mean[Var, 2]` (`r corrire[[1]]$PI$lower[Var, 2]`-`r corrire[[1]]$PI$upper[Var, 2]`) <br> **`r corrire[[1]]$real[Var, 2]`** | `r indep[[1]]$mean[Var, 3]` (`r indep[[1]]$PI$lower[Var, 3]`-`r indep[[1]]$PI$upper[Var, 3]`) <br> `r corr[[1]]$mean[Var, 3]` (`r corr[[1]]$PI$lower[Var, 3]`-`r corr[[1]]$PI$upper[Var, 3]`) <br> `r corrire[[1]]$mean[Var, 3]` (`r corrire[[1]]$PI$lower[Var, 3]`-`r corrire[[1]]$PI$upper[Var, 3]`) <br> **`r corrire[[1]]$real[Var, 3]`** | `r indep[[1]]$mean[Var, 4]` (`r indep[[1]]$PI$lower[Var, 4]`-`r indep[[1]]$PI$upper[Var, 4]`) <br> `r corr[[1]]$mean[Var, 4]` (`r corr[[1]]$PI$lower[Var, 4]`-`r corr[[1]]$PI$upper[Var, 4]`) <br> `r corrire[[1]]$mean[Var, 4]` (`r corrire[[1]]$PI$lower[Var, 4]`-`r corrire[[1]]$PI$upper[Var, 4]`) <br> **`r corrire[[1]]$real[Var, 4]`** |
| **Alicante**        | `r indep[[2]]$mean[Var, 1]` (`r indep[[2]]$PI$lower[Var, 1]`-`r indep[[2]]$PI$upper[Var, 1]`) <br> `r corr[[2]]$mean[Var, 1]` (`r corr[[2]]$PI$lower[Var, 1]`-`r corr[[2]]$PI$upper[Var, 1]`) <br> `r corrire[[2]]$mean[Var, 1]` (`r corrire[[2]]$PI$lower[Var, 1]`-`r corrire[[2]]$PI$upper[Var, 1]`) <br> **`r corrire[[2]]$real[Var, 1]`** | `r indep[[2]]$mean[Var, 2]` (`r indep[[2]]$PI$lower[Var, 2]`-`r indep[[2]]$PI$upper[Var, 2]`) <br> `r corr[[2]]$mean[Var, 2]` (`r corr[[2]]$PI$lower[Var, 2]`-`r corr[[2]]$PI$upper[Var, 2]`) <br> `r corrire[[2]]$mean[Var, 2]` (`r corrire[[2]]$PI$lower[Var, 2]`-`r corrire[[2]]$PI$upper[Var, 2]`) <br> **`r corrire[[2]]$real[Var, 2]`** | `r indep[[2]]$mean[Var, 3]` (`r indep[[2]]$PI$lower[Var, 3]`-`r indep[[2]]$PI$upper[Var, 3]`) <br> `r corr[[2]]$mean[Var, 3]` (`r corr[[2]]$PI$lower[Var, 3]`-`r corr[[2]]$PI$upper[Var, 3]`) <br> `r corrire[[2]]$mean[Var, 3]` (`r corrire[[2]]$PI$lower[Var, 3]`-`r corrire[[2]]$PI$upper[Var, 3]`) <br> **`r corrire[[2]]$real[Var, 3]`** | `r indep[[2]]$mean[Var, 4]` (`r indep[[2]]$PI$lower[Var, 4]`-`r indep[[2]]$PI$upper[Var, 4]`) <br> `r corr[[2]]$mean[Var, 4]` (`r corr[[2]]$PI$lower[Var, 4]`-`r corr[[2]]$PI$upper[Var, 4]`) <br> `r corrire[[2]]$mean[Var, 4]` (`r corrire[[2]]$PI$lower[Var, 4]`-`r corrire[[2]]$PI$upper[Var, 4]`) <br> **`r corrire[[2]]$real[Var, 4]`** |
| **Elche**           | `r indep[[3]]$mean[Var, 1]` (`r indep[[3]]$PI$lower[Var, 1]`-`r indep[[3]]$PI$upper[Var, 1]`) <br> `r corr[[3]]$mean[Var, 1]` (`r corr[[3]]$PI$lower[Var, 1]`-`r corr[[3]]$PI$upper[Var, 1]`) <br> `r corrire[[3]]$mean[Var, 1]` (`r corrire[[3]]$PI$lower[Var, 1]`-`r corrire[[3]]$PI$upper[Var, 1]`) <br> **`r corrire[[3]]$real[Var, 1]`** | `r indep[[3]]$mean[Var, 2]` (`r indep[[3]]$PI$lower[Var, 2]`-`r indep[[3]]$PI$upper[Var, 2]`) <br> `r corr[[3]]$mean[Var, 2]` (`r corr[[3]]$PI$lower[Var, 2]`-`r corr[[3]]$PI$upper[Var, 2]`) <br> `r corrire[[3]]$mean[Var, 2]` (`r corrire[[3]]$PI$lower[Var, 2]`-`r corrire[[3]]$PI$upper[Var, 2]`) <br> **`r corrire[[3]]$real[Var, 2]`** | `r indep[[3]]$mean[Var, 3]` (`r indep[[3]]$PI$lower[Var, 3]`-`r indep[[3]]$PI$upper[Var, 3]`) <br> `r corr[[3]]$mean[Var, 3]` (`r corr[[3]]$PI$lower[Var, 3]`-`r corr[[3]]$PI$upper[Var, 3]`) <br> `r corrire[[3]]$mean[Var, 3]` (`r corrire[[3]]$PI$lower[Var, 3]`-`r corrire[[3]]$PI$upper[Var, 3]`) <br> **`r corrire[[3]]$real[Var, 3]`** | `r indep[[3]]$mean[Var, 4]` (`r indep[[3]]$PI$lower[Var, 4]`-`r indep[[3]]$PI$upper[Var, 4]`) <br> `r corr[[3]]$mean[Var, 4]` (`r corr[[3]]$PI$lower[Var, 4]`-`r corr[[3]]$PI$upper[Var, 4]`) <br> `r corrire[[3]]$mean[Var, 4]` (`r corrire[[3]]$PI$lower[Var, 4]`-`r corrire[[3]]$PI$upper[Var, 4]`) <br> **`r corrire[[3]]$real[Var, 4]`** |
| **Castellón de la Plana** | `r indep[[4]]$mean[Var, 1]` (`r indep[[4]]$PI$lower[Var, 1]`-`r indep[[4]]$PI$upper[Var, 1]`) <br> `r corr[[4]]$mean[Var, 1]` (`r corr[[4]]$PI$lower[Var, 1]`-`r corr[[4]]$PI$upper[Var, 1]`) <br> `r corrire[[4]]$mean[Var, 1]` (`r corrire[[4]]$PI$lower[Var, 1]`-`r corrire[[4]]$PI$upper[Var, 1]`) <br> **`r corrire[[4]]$real[Var, 1]`** | `r indep[[4]]$mean[Var, 2]` (`r indep[[4]]$PI$lower[Var, 2]`-`r indep[[4]]$PI$upper[Var, 2]`) <br> `r corr[[4]]$mean[Var, 2]` (`r corr[[4]]$PI$lower[Var, 2]`-`r corr[[4]]$PI$upper[Var, 2]`) <br> `r corrire[[4]]$mean[Var, 2]` (`r corrire[[4]]$PI$lower[Var, 2]`-`r corrire[[4]]$PI$upper[Var, 2]`) <br> **`r corrire[[4]]$real[Var, 2]`** | `r indep[[4]]$mean[Var, 3]` (`r indep[[4]]$PI$lower[Var, 3]`-`r indep[[4]]$PI$upper[Var, 3]`) <br> `r corr[[4]]$mean[Var, 3]` (`r corr[[4]]$PI$lower[Var, 3]`-`r corr[[4]]$PI$upper[Var, 3]`) <br> `r corrire[[4]]$mean[Var, 3]` (`r corrire[[4]]$PI$lower[Var, 3]`-`r corrire[[4]]$PI$upper[Var, 3]`) <br> **`r corrire[[4]]$real[Var, 3]`** | `r indep[[4]]$mean[Var, 4]` (`r indep[[4]]$PI$lower[Var, 4]`-`r indep[[4]]$PI$upper[Var, 4]`) <br> `r corr[[4]]$mean[Var, 4]` (`r corr[[4]]$PI$lower[Var, 4]`-`r corr[[4]]$PI$upper[Var, 4]`) <br> `r corrire[[4]]$mean[Var, 4]` (`r corrire[[4]]$PI$lower[Var, 4]`-`r corrire[[4]]$PI$upper[Var, 4]`) <br> **`r corrire[[4]]$real[Var, 4]`** |
| **Orihuela**        | `r indep[[5]]$mean[Var, 1]` (`r indep[[5]]$PI$lower[Var, 1]`-`r indep[[5]]$PI$upper[Var, 1]`) <br> `r corr[[5]]$mean[Var, 1]` (`r corr[[5]]$PI$lower[Var, 1]`-`r corr[[5]]$PI$upper[Var, 1]`) <br> `r corrire[[5]]$mean[Var, 1]` (`r corrire[[5]]$PI$lower[Var, 1]`-`r corrire[[5]]$PI$upper[Var, 1]`) <br> **`r corrire[[5]]$real[Var, 1]`** | `r indep[[5]]$mean[Var, 2]` (`r indep[[5]]$PI$lower[Var, 2]`-`r indep[[5]]$PI$upper[Var, 2]`) <br> `r corr[[5]]$mean[Var, 2]` (`r corr[[5]]$PI$lower[Var, 2]`-`r corr[[5]]$PI$upper[Var, 2]`) <br> `r corrire[[5]]$mean[Var, 2]` (`r corrire[[5]]$PI$lower[Var, 2]`-`r corrire[[5]]$PI$upper[Var, 2]`) <br> **`r corrire[[5]]$real[Var, 2]`** | `r indep[[5]]$mean[Var, 3]` (`r indep[[5]]$PI$lower[Var, 3]`-`r indep[[5]]$PI$upper[Var, 3]`) <br> `r corr[[5]]$mean[Var, 3]` (`r corr[[5]]$PI$lower[Var, 3]`-`r corr[[5]]$PI$upper[Var, 3]`) <br> `r corrire[[5]]$mean[Var, 3]` (`r corrire[[5]]$PI$lower[Var, 3]`-`r corrire[[5]]$PI$upper[Var, 3]`) <br> **`r corrire[[5]]$real[Var, 3]`** | `r indep[[5]]$mean[Var, 4]` (`r indep[[5]]$PI$lower[Var, 4]`-`r indep[[5]]$PI$upper[Var, 4]`) <br> `r corr[[5]]$mean[Var, 4]` (`r corr[[5]]$PI$lower[Var, 4]`-`r corr[[5]]$PI$upper[Var, 4]`) <br> `r corrire[[5]]$mean[Var, 4]` (`r corrire[[5]]$PI$lower[Var, 4]`-`r corrire[[5]]$PI$upper[Var, 4]`) <br> **`r corrire[[5]]$real[Var, 4]`** |
| **Torrevieja**        | `r indep[[6]]$mean[Var, 1]` (`r indep[[6]]$PI$lower[Var, 1]`-`r indep[[6]]$PI$upper[Var, 1]`) <br> `r corr[[6]]$mean[Var, 1]` (`r corr[[6]]$PI$lower[Var, 1]`-`r corr[[6]]$PI$upper[Var, 1]`) <br> `r corrire[[6]]$mean[Var, 1]` (`r corrire[[6]]$PI$lower[Var, 1]`-`r corrire[[6]]$PI$upper[Var, 1]`) <br> **`r corrire[[6]]$real[Var, 1]`** | `r indep[[6]]$mean[Var, 2]` (`r indep[[6]]$PI$lower[Var, 2]`-`r indep[[6]]$PI$upper[Var, 2]`) <br> `r corr[[6]]$mean[Var, 2]` (`r corr[[6]]$PI$lower[Var, 2]`-`r corr[[6]]$PI$upper[Var, 2]`) <br> `r corrire[[6]]$mean[Var, 2]` (`r corrire[[6]]$PI$lower[Var, 2]`-`r corrire[[6]]$PI$upper[Var, 2]`) <br> **`r corrire[[6]]$real[Var, 2]`** | `r indep[[6]]$mean[Var, 3]` (`r indep[[6]]$PI$lower[Var, 3]`-`r indep[[6]]$PI$upper[Var, 3]`) <br> `r corr[[6]]$mean[Var, 3]` (`r corr[[6]]$PI$lower[Var, 3]`-`r corr[[6]]$PI$upper[Var, 3]`) <br> `r corrire[[6]]$mean[Var, 3]` (`r corrire[[6]]$PI$lower[Var, 3]`-`r corrire[[6]]$PI$upper[Var, 3]`) <br> **`r corrire[[6]]$real[Var, 3]`** | `r indep[[6]]$mean[Var, 4]` (`r indep[[6]]$PI$lower[Var, 4]`-`r indep[[6]]$PI$upper[Var, 4]`) <br> `r corr[[6]]$mean[Var, 4]` (`r corr[[6]]$PI$lower[Var, 4]`-`r corr[[6]]$PI$upper[Var, 4]`) <br> `r corrire[[6]]$mean[Var, 4]` (`r corrire[[6]]$PI$lower[Var, 4]`-`r corrire[[6]]$PI$upper[Var, 4]`) <br> **`r corrire[[6]]$real[Var, 4]`** |

*Note:* Posterior means, (95% prediction intervals) and observed values (**in bold**) of the percentage of respondents in each category for some municipalities in the RV.

